---
title: "EugeneTest"
author: "Eugene Lim"
date: "11/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("EugeneWorkPlace.R")
library(dplyr)
library(ggplot2)
library(plotly)
library(knitr)
library(leaflet)
library(tigris)
```

```{r interactive_map, echo = FALSE}
states_merged <- geo_join(states, us_states, "STUSPS", "What.US.state.or.territory.do.you.live.in")  
pal <- colorNumeric("Greens", domain = affected$total_affected)
leaflet(states) %>%
  addProviderTiles("CartoDB.Positron") %>%
  setView(lng = -99.62679, lat = 39.11553, zoom = 4.4) %>%
  addPolygons(data = states_merged,
              fillColor = 
                ~pal(affected$total_affected),
              fillOpacity = 0.7,
              weight = 0.2,
              smoothFactor = 0.2,
              popup = ~paste0("State: ", NAME, "<br># People With Mental Illness: ", affected$total_affected)) %>%
  addLegend(pal = pal,
            values = affected$total_affected,
            position = "bottomright",
            title = "Mental Illness Present")
```

##3.0:
OSMI Mental Health Dataset: This data set has 30 columns and 59,535 rows of observations. This data set that we originally found on data.world is gathered from a yearly survey hosted by OSMI, a non-profit organization researching mental illness in the tech and open-source communities. The survey results were collected from March 2017. An observation is an individual participating in the survey. There are variable such as location, age, if they are experience mental illness and etc. This dataset could be stronger if it incorporated surveys from other careers like art or education. 

In data wrangling, we cleaned the data so that only survey results from the United States were left. We excluded missing values for country and state. 


##4.0: 
We decided to create an interactive map that displays the state statistics of how many people are dealing with a mental illness currently. We plan to also show the three biggest mental illnesses in each state and the percentage of male to females as well. In this manner, the visual would line up with our research questions.

